---
title: "Census and ACS data on Browns Addition"
output: html_notebook
---

Variables of interest 

-Population/Gender
-Race/Ethnicity
- BEN is beautifu
-Age
-Family Status (couples/kids)
-Education (access; graduation rates; school lunch program activity; students experiencing homelessness report; early learning; post-grad)
-Employment/SES/Economy (access to jobs; unemployment levels; types of jobs; business/factories; income/poverty levels; underground economy)
-Housing Status & Availability (homeowners vs. renters v. homeless)
-Health (of individuals; access; physical and mental health facilities; service providers (formal and informal; health management)


```{r}

library(tidycensus)
library(tidyverse)
library(viridis)
library(mapview)
census_api_key("768764eb83f54797347a477143a2d37d893fe93e")

spo <- get_acs(geography = "block group", 
                variables = "B01003_001", 
                state = "WA", 
                county = "Spokane", 
                geometry = TRUE)


mapview(spo, zcol = "estimate")


```


```{r}

spo %>% 
  as_tibble() %>% 
  filter(str_detect(NAME, "(Group 1)|(Group 3)"), 
         str_detect(NAME, "Tract 36")) %>% 
  summarise(population = sum(estimate), 
            moe = moe_sum(moe, estimate = estimate))


```



TODO 

add variables
add citations
